MergeBiomarkWith10X

### 2021-10-08 MergeBiomarkWith10X/MergeBiomarkWith10X.Rmd
Generate GSEA lists for Biomark and 10X merging

# Setup
```{r setup}
knitr::opts_knit$set(root.dir = "~/Desktop/10XGenomicsData/msAggr_scRNASeq/MergeBiomarkWith10X/")
```

@@

## Set global variables
```{r}
pop.of.interest <- "CMP"
cellranger.folder <- "m2"
fav.var <- 95
object.res <- ".0.5"
ident.list <- c("integrated_snn_res.0.5", "integrated_snn_res.1")
projectName <- paste0("MergeBiomarkWith10X_", pop.of.interest)
```

```{r}
source("~/Desktop/10XGenomicsData/msAggr_scRNASeq/RFunctions/ColorPalette.R")
source("~/Desktop/10XGenomicsData/msAggr_scRNASeq/RFunctions/PercentVariance.R")
source("~/Desktop/10XGenomicsData/msAggr_scRNASeq/RFunctions/read_10XGenomics_data.R")
source("~/Desktop/10XGenomicsData/msAggr_scRNASeq/RFunctions/Mouse2Human_idconversion.R")
```
store session info
```{r }
sink(paste0(projectName, "_sessionInfo.txt"))
sessionInfo()
sink()
```

@@

```{r}
pseudo.biomark.T[is.na(pseudo.biomark.T)] <- 0
pseudo.biomark.T <- as.sparse(pseudo.biomark.T)
biomark.object <- CreateSeuratObject(pseudo.biomark.T, project = "Biomark", assay = "RNA", meta.data = biomark.meta)
```

@@

## merge objects
```{r}
seurat.object <- merge(sc.object, biomark.object, project = 'mergebiomark')
seurat.object@meta.data$orig.ident[seurat.object@meta.data$orig.ident == paste0(pop.of.interest, cellranger.folder)] <- '10X'
seurat.object@meta.data$orig.ident[seurat.object@meta.data$orig.ident == pop.of.interest] <- 'Biomark'
# seurat.object@meta.data[is.na(seurat.object@meta.data)] <- 0
# seurat.object@meta.data$orig.ident <- factor(seurat.object@meta.data$orig.ident)
# seurat.object@meta.data$pid <- factor(seurat.object@meta.data$pid)
# seurat.object@meta.data$wid <- factor(seurat.object@meta.data$wid)
seurat.object
```

@@

### Save merged object
```{r}
saveRDS(seurat.object, file = paste0(projectName, "_raw.RDS"))
```
## Run PCA
```{r}
seurat.object <- RunPCA(seurat.object, ndims.print = 1:5, nfeatures.print = 5, features = all.genes)
```

@@

## identify anchors
```{r}

tech.anchors <- FindIntegrationAnchors(object.list = tech.list, anchor.features = all.genes, k.anchor = 20, k.filter = NA)
# tech.integrated <- IntegrateData(anchorset = tech.anchors, dims = 1:30, k.weight = 20, normalization.method = "SCT")
tech.integrated <- IntegrateData(anchorset = tech.anchors, k.weight = 5)
```

@@

	}
}
```
### Evaluate cluster stability
```{r fig.height=5}
clustree(tech.integrated, prefix = "integrated_snn_res.", node_colour = "sc3_stability") + 
	scale_color_continuous(low = 'red3', high = 'white')
png(filename = paste0(projectName, "_pctVar", pct.var, "-clustree.png"), height = 800, width = 1600)
clustree(tech.integrated, prefix = "integrated_snn_res.", node_colour = "sc3_stability") +
	scale_color_continuous(low = 'red3', high = 'white')
dev.off()
```

@@

## Reload object 
```{r}
tech.integrated <- readRDS(paste0(projectName, "_pctVar", fav.var, ".RDS"))
tech.integrated <- SetIdent(tech.integrated, value = paste0("integrated_snn_res", object.res))
```

for each resolution, number/percentage of cells in each cluster?

```{r}
tot.cells <- nrow(tech.integrated@meta.data)
for (meta.col in colnames(tech.integrated@meta.data)){
	if(grepl(pattern = ("integrated_snn_res"), x = meta.col)==TRUE){
		new.clusters <- sort(as.numeric(levels(tech.integrated@meta.data[[meta.col]])))
		stats.df <- data.frame(matrix(ncol = 2, nrow = length(new.clusters)))
		colnames(stats.df) <- c("num_cells", "pct_pop")
		rownames(stats.df) <- new.clusters
		meta.df <- tech.integrated@meta.data
		for(row.id in rownames(stats.df)){
			num.x <- nrow(meta.df[meta.df[meta.col] == row.id,])
			pct.x <- as.integer(num.x / tot.cells *100)
			# print(pct.x)
			stats.df[row.id, "num_cells"] <- num.x
			stats.df[row.id, "pct_pop"] <- pct.x
		}
		print(stats.df)
	}
}
```
```{r}
tech.integrated <- readRDS("")
```

```{r}
current_res <- 'integrated_snn_res.0.5'
tech.integrated@meta.data$orig.ident[tech.integrated@meta.data$orig.ident == paste0(pop.of.interest, cellranger.folder)] <- "10X"
tech.integrated@meta.data$orig.ident[tech.integrated@meta.data$orig.ident == paste0(pop.of.interest)] <- "biomark"
tech.integrated@meta.data$orig.ident <- factor(tech.integrated@meta.data$orig.ident)

@@

## Create `FindAllMarkers()` lists for GSEA
```{r}
ident.list <- c("integrated_snn_res.0.5")

@@

HGNC <- with(Mouse2HumanTable, Mouse2HumanTable$HGNC[match(object.res.allmarkers$gene, Mouse2HumanTable$MGI)])
head(object.res.allmarkers)
object.res.allmarkers$HGNC <- HGNC
tail(object.res.allmarkers)
sig.res <- object.res.allmarkers[object.res.allmarkers$p_val_adj <= 0.05, ]
sig.res <- sig.res[c("avg_log2FC", "HGNC", "cluster")]
sig.res <- sig.res[!(sig.res$HGNC == "" | is.na(sig.res$HGNC)),] # GSEA will fail if there are any blanks or NAs in the table
sig.res <- sig.res[]

```{r}
for(cluster in unique(sig.res$cluster)){
	print(paste("writing cluster", cluster))
	new.table <- sig.res[sig.res$cluster == cluster, c("HGNC", "avg_log2FC")]
	new.table <- new.table[order(-new.table$avg_log2FC), ]
	try(dir.create(paste0("RankList_pctVar", pct.var, "res", object.res, "_findAll_hgnc/"), showWarnings = FALSE))
	try(write.table(new.table, file = paste0("RankList_pctVar", pct.var, "res", object.res, "_findAll_hgnc/", projectName, "pctVar", pct.var, "res", object.res, "cluster", cluster, ".rnk"), quote = FALSE, row.names = FALSE, col.names = TRUE, sep = "\t", ))

>>>>

# Setup
```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir = "~/Desktop/10XGenomicsData/msAggr_scRNASeq/MergeBiomarkWith10X/")
```

@@

## Set global variables
```{r}
pop.of.interest <- "LSK"
cellranger.folder <- "m2"
fav.var <- 95
object.res <- ".0.5"
ident.list <- c("integrated_snn_res.0.5", "integrated_snn_res.1")
projectName <- paste0("MergeBiomarkWith10X_", pop.of.interest)
```
source code
```{r}
source("~/Desktop/10XGenomicsData/msAggr_scRNASeq/RFunctions/ColorPalette.R")
source("~/Desktop/10XGenomicsData/msAggr_scRNASeq/RFunctions/PercentVariance.R")
source("~/Desktop/10XGenomicsData/msAggr_scRNASeq/RFunctions/read_10XGenomics_data.R")
source("~/Desktop/10XGenomicsData/msAggr_scRNASeq/RFunctions/Mouse2Human_idconversion.R")
```
store session info
```{r }
sink(paste0(projectName, "_sessionInfo.txt"))
sessionInfo()
sink()
```

@@

```{r}
pseudo.biomark.T[is.na(pseudo.biomark.T)] <- 0
pseudo.biomark.T <- as.sparse(pseudo.biomark.T)
biomark.object <- CreateSeuratObject(pseudo.biomark.T, project = "biomark", assay = "RNA", meta.data = biomark.meta)
```

@@

## merge objects
```{r}
seurat.object <- merge(sc.object, biomark.object, project = 'mergebiomark')
seurat.object@meta.data$orig.ident[seurat.object@meta.data$orig.ident == paste0(pop.of.interest, cellranger.folder)] <- '10X'
seurat.object@meta.data$orig.ident[seurat.object@meta.data$orig.ident == pop.of.interest] <- 'biomark'
# seurat.object@meta.data[is.na(seurat.object@meta.data)] <- 0
# seurat.object@meta.data$orig.ident <- factor(seurat.object@meta.data$orig.ident)
# seurat.object@meta.data$pid <- factor(seurat.object@meta.data$pid)
# seurat.object@meta.data$wid <- factor(seurat.object@meta.data$wid)
seurat.object
```

@@

### Save merged object
```{r}
# saveRDS(seurat.object, file = paste0(projectName, "_raw.RDS"))
```
## Run PCA
```{r}
seurat.object <- RunPCA(seurat.object, ndims.print = 1:5, nfeatures.print = 5, features = all.genes)
```

@@

## identify anchors
```{r}
tech.anchors <- FindIntegrationAnchors(object.list = tech.list, anchor.features = all.genes, k.anchor = 20, k.filter = NA)
# tech.integrated <- IntegrateData(anchorset = tech.anchors, dims = 1:30, k.weight = 20, normalization.method = "SCT")
tech.integrated <- IntegrateData(anchorset = tech.anchors, k.weight = 5)
```

@@

	}
}
```
### Evaluate cluster stability
```{r fig.height=5}
clustree(tech.integrated, prefix = "integrated_snn_res.", node_colour = "sc3_stability") + 
	scale_color_continuous(low = 'red3', high = 'white')
png(filename = paste0(projectName, "_pctVar", pct.var, "-clustree.png"), height = 800, width = 1600)
clustree(tech.integrated, prefix = "integrated_snn_res.", node_colour = "sc3_stability") +
	scale_color_continuous(low = 'red3', high = 'white')
dev.off()
```
```{r}
saveRDS(tech.integrated, file = paste0(projectName, "_pctVar", pct.var, ".RDS"))
```

@@

## Reload object 
```{r}
tech.integrated <- readRDS(paste0(projectName, "_pctVar", fav.var, ".RDS"))
tech.integrated <- SetIdent(tech.integrated, value = paste0("integrated_snn_res", object.res))
```
for each resolution, number/percentage of cells in each cluster?
```{r}
current_res <- 'integrated_snn_res.0.5'
tech.integrated@meta.data$orig.ident[tech.integrated@meta.data$orig.ident == paste0(pop.of.interest, cellranger.folder)] <- "10X"
tech.integrated@meta.data$orig.ident[tech.integrated@meta.data$orig.ident == paste0(pop.of.interest)] <- "biomark"
tech.integrated@meta.data$orig.ident <- factor(tech.integrated@meta.data$orig.ident)

@@

## Create `FindAllMarkers()` lists for GSEA
```{r}
ident.list <- c(paste0("integrated_snn_res", object.res))

@@

HGNC <- with(Mouse2HumanTable, Mouse2HumanTable$HGNC[match(object.res.allmarkers$gene, Mouse2HumanTable$MGI)])
head(object.res.allmarkers)
object.res.allmarkers$HGNC <- HGNC
# tail(object.res.allmarkers)
sig.res <- object.res.allmarkers[object.res.allmarkers$p_val_adj <= 0.05, ]
sig.res <- sig.res[c("avg_log2FC", "HGNC", "cluster")]
sig.res <- sig.res[!(sig.res$HGNC == "" | is.na(sig.res$HGNC)),] # GSEA will fail if there are any blanks or NAs in the table
sig.res <- sig.res[]

for(cluster in unique(sig.res$cluster)){
	print(paste("writing cluster", cluster))
	new.table <- sig.res[sig.res$cluster == cluster, c("HGNC", "avg_log2FC")]
	new.table <- new.table[order(-new.table$avg_log2FC), ]
	try(dir.create(paste0("RankList_findAll_hgnc/"), showWarnings = FALSE))
	try(write.table(new.table, file = paste0("RankList_findAll_hgnc/", projectName, "pctVar", pct.var, "res", object.res, "cluster", cluster, ".rnk"), quote = FALSE, row.names = FALSE, col.names = TRUE, sep = "\t", ))
